First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2019-12-06 MY_PUBLICATIONS/PRL/draft_v1/prl.tex
updated

%CURRENTLY CORRECTING
\begin{abstract}
  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at 4-momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 GeV$^{2}$ for 
  neutron recoil momenta up to $p_{r}\sim$1.18 GeV/c and neutron recoil angles ($\theta_{nq}$) of 35, 45 and 75 degrees are presented. At the selected kinematics,
  Meson Exchange Currents (MEC) and Isobar Configurations (IC) are suppressed. At recoil angles of 35 and 45 degrees, Final State Interactions (FSI) have been suppressed
  and the Plane Wave Impulse Approximation (PWIA) provides the dominant cross section contribution. A comparison to recent theoretical calculations show the data to be sensitive
  to momentum distributions up to $p_{r}\sim$ 750 MeV/c.
\end{abstract}

>>>>

\begin{abstract}
  New $^{2}H(e,e'p)n$ cross sections have been measured at 4-momentum transfers $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
  for neutron recoil (missing) momenta up $p_{r}\sim$ 1.18 GeV/c at several fixed neutron recoil angles ($\theta_{nq}$)
  with respect to the 3-momentum transfer, $\vec{q}$. At neutron angles of 35 and 45 degrees final state interactions (FSIs) as well as
  meson exchange currents (MECs) and isobar configurations (ICs) are expected to be suppressed and the plane wave impulse
  approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent theoretical
  calculations where significant disagreement at very high missing momenta has been observed.
\end{abstract}
